Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Paper restructure

\newcommand\mahmoud[1]{\color{green}\textbf{\\ Mahmoud: #1}\\\color{black}}
\newcommand\stefan[1]{\color{blue}\textbf{\\ Stefan: #1}\color{black}}
\newcommand\maciek[1]{\color{brown}\textbf{\\ Maciek: #1}\color{black}}

@@

\maciek{Example figure of the construction and growing components.}

@@

@@

\maciek{Figure: cluster signatures}

\maciek{Figure: an unsaturated edge that is inside a component}

@@

@@

\section{Maciek's sketches}

\begin{theorem}
  Algorithm DET2 is $O(\ell \cdot k\cdot k^k)$-competitive.
\end{theorem}

\begin{proof}
  Use Theorem~\ref{th:cascade}. Then, linearize the inner-component communication using the technique from SIDMA.
\end{proof}

>>>>

\newcommand\mahmoud[1]{\color{green}\textbf{\\ Mahmoud: #1}\\\color{black}}
\newcommand\stefan[1]{\color{blue}\textbf{\\ Stefan: #1}\color{black}}
\newcommand\maciek[1]{\color{brown}\textbf{\\ Maciek: #1}\color{black}}
%\newcommand\maciek[1]{}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.3\textwidth]{figs/substitute}
    \caption{Example figure of the construction of the LB and growing components.}
    \label{fig:nptree-construction}
  \end{figure}

@@

\maciek{Rewrite above paragraph to say that our algorithm is essentially DET from DISC16, with concretised reconfiguration strategy (i.e., the cheapest)}

\subsection{Improved analysis of the component-based algorithm}

@@

  \begin{figure}[H]
    \centering
      \includegraphics[width=0.3\textwidth]{figs/substitute}
      \caption{an unsaturated edge that is inside a component}
    \end{figure}

@@

\section{Bounding the cost of a single reconfiguration}

\subsection{Warm-up: bounding the reconfiguration for $k=3$}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.3\textwidth]{figs/substitute}
    \caption{Cluster signatures in warm-up k=3 proof}
  \end{figure}

\subsection{Characterization of the reconfiguration graph}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.3\textwidth]{figs/substitute}
    \caption{Illustration to bounding the path length.}
    \label{fig:nptree-construction}
  \end{figure}

Corollary: Algorithm DET2 is $O(\ell \cdot k\cdot k^k)$-competitive.

\section{Improved algorithm for $k=2$}

@@
